Revisiting divisible, injective and flabby abelian groups from a constructive point of view

### 2022-09-30 slides-fischbachau2022.tex
typo

  \textbf{Thm.} Let~$X$ be an inhabited set of natural numbers.
  \begin{enumerate}
    \item Assuming~\badbox{\textsc{lem}}, the set~$X$ contains a minimal element.
    \item<5-> If~$X$ is \hil{detachable}, then~$X$ contains a minimal element.
    \item<7-> It is \hil{not~not} the case that~$X$ contains a minimal element.
  \end{enumerate}

@@

  \begin{itemize}
    \item empty list: $[]$
    \item extension: $[x_1,\ldots,x_n] ::^r x_{n+1} = [x_1,\ldots,x_n,x_{n+1}]$
    \item refinement relation: $[x_1,\ldots,x_n,x_{n+1},x_{n+m}] \preceq [x_1,\ldots,x_n]$
    \item element access: $\sigma[i] = \text{element at position~$i$
    in~$\sigma$}$
  \end{itemize}
  \justifying

@@

  \textbf{Ex.} $(\forall^{x\?X}\_ \exists^{n\?\NN}\_ \genalpha(n){=}x)^\nabla
  \equiv$ \\
  $\qquad\qquad
    (\forall^{x\?X}\_ \nabla^{\tau\preceq\sigma}\_
    \exists^{n\?\NN}\_
    \nabla^{\upsilon\preceq\tau}\_ (\textsf{len}(\upsilon) > n \wedge \upsilon[n] = x))$

  \textbf{Thm.} [Joyal--Tierney 1984] For \hil{first-order} formulas~$\varphi$,
  $\varphi^\nabla \Rightarrow \varphi$.
\end{frame}

>>>>

  \textbf{Lemma.} Let~$X$ be an inhabited set of natural numbers.
  \begin{enumerate}
    \item Assuming~\badbox{\textsc{lem}}, the set~$X$ contains a minimal element.
    \item<5-> If~$X$ is \hil{detachable}, then~$X$ contains a minimal element.
    \item<7-> It is \hil{not~not} the case that~$X$ contains a minimal element.
  \end{enumerate}

@@

  \begin{itemize}
    \item empty list: $[]$
    \item extension: $[x_1,\ldots,x_n] ::^r x_{n+1} = [x_1,\ldots,x_n,x_{n+1}]$
    \item refinement relation: $[x_1,\ldots,x_n,x_{n+1},x_{n+m}] \preceq [x_1,\ldots,x_n]$
    \item element access: $\sigma[i] = \text{element at position~$i$
    in~$\sigma$}$
  \end{itemize}
  \justifying
  \pause

@@

  \vspace*{-0.3em}
  \textbf{Ex.} $(\forall^{x\?X}\_ \exists^{n\?\NN}\_ \genalpha(n){=}x)^\nabla
  \equiv$ \\
  $\qquad\qquad
    (\forall^{x\?X}\_ \nabla^{\tau\preceq\sigma}\_
    \exists^{n\?\NN}\_
    \nabla^{\upsilon\preceq\tau}\_ (\textsf{len}(\upsilon) > n \wedge \upsilon[n] = x)).$

  \vspace*{-0.3em}
  \textbf{Thm.} [Joyal--Tierney 1984] For \hil{first-order} formulas~$\varphi$
  not referring to~$\genalpha$, $\varphi^\nabla \Rightarrow \varphi$
  intuitionistically.
\end{frame}
